Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-04 Latex/tex/pr.tex
latex part 3 or 4

@@

Therefore, the mean arrival data rate of UEs in $s^{th}$ slice is 
$\alpha_s = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}\lambda_{u(v,i)}$.  

@@

>>>>

\subsection{Mean Delay}

@@

Therefore, the mean arrival data rate of UEs in $s^{th}$ slice in the first layer is 
$\alpha_{s_1} = \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}\lambda_{u(v,i)}$.  
Furthermore, the mean arrival rate of second layer is approximately equal to the mean arrival rate of first layer $\alpha_{s} =\alpha_{s_1} \approx \alpha_{s_2}$ since, by using Burke’s Theorem, the arrival packets of second layer which is processed in first layer is still Poisson with rate $\alpha_{s}$  

@@

Each packet is routed by one of VMs of slices. So the mean delay of slice $s$ which is related to incoming traffic rate routed to
each VM in first layer can be written as follow
d_{s_1} = \frac{1}{\mu_1 - \alpha_{s}/{M_{s_1}}}
Also, the delay in $s^{th}$ slice in second layer can be formulated as below
d_{s_2} = \frac{1}{\mu_2 - \alpha_{s}/{M_{s_2}}}
In addition, the arrival data rate to the queue of wireless transmission
 is equal to the arrival data rate of dispatcher.
Moreover, it is assumed that the service time of transmission queue for each slice $s$ has 
 an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue. Therefore, 
the mean delay of transmission layer is 
d_{s_{tr}} = \frac{1}{R_{{tot}_s} - \alpha_{s}}
Where, $R_{{tot}_s} =  \sum_{v=1}^{V}\sum_{u=2}^{U_v}a_{vs}R_{u(v,i)}$.
\subsection{Physical Resource}
Assume that for simplicity, each VM is mapped to one virtual network function (VNF). Each VNF requires
physical resources which contain RAM, Memory and CPU.
Let, the required resources for VNF $f$ in slice $s$ is represented by
\Omega_{(f,s)} = \{\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}} \}
Where, $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory and CPU.
Also, in the Core Network(CN), there are $N_{D}$ data centers(DC), which served VNFs. Each DC contains several servers that supply VNF's needs.
The amount of RAM, Memory and CPU is denoted respectively by $\tau_{R_{j}}, \tau_{M_{j}}$ and $\tau_{C_{j}} $ for $j^{th}$ DC.
\subsection{Problem Formulation}
